\newpage
\chapter{Real Estate Blockchain Projects Compared}
While many real estate platforms claim blockchain innovation, most fall short of its foundational ideals. As outlined by Andreas M. Antonopoulos in \textit{The Internet of Money}, a true blockchain system should deliver decentralization, trustless validation, permissionless access, user sovereignty, and elimination of intermediaries.

Most solutions merely bolt blockchain onto legacy systems, preserving traditional power structures. This evaluation highlights key projects based on core decentralization principles:

\begin{table}[H]
\centering
\scriptsize
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{|p{1.4cm}|p{2.3cm}|p{2.3cm}|p{2.3cm}|p{2.3cm}|p{1.8cm}|}
\hline
\textbf{Project} & \textbf{Decentralization} & \textbf{Trustless Validation} & \textbf{Permissionless Access} & \textbf{Middleman Elimination} & \textbf{Alignment} \\
\hline
\textbf{Elephant} & 
\textcolor{green}{$\checkmark$} Full oracle network with staking \& slashing & 
\textcolor{green}{$\checkmark$} Cryptographic proofs, immutable record & 
\textcolor{green}{$\checkmark$} Anyone can verify/earn & 
\textcolor{green}{$\checkmark$} Removes \$234B in friction & 
\textcolor{green}{\textbf{Fully aligned}} \\
\hline
\textbf{Propy} & 
\textcolor{red}{$\times$} Hybrid: relies on agents & 
\textcolor{orange}{$\sim$} Blockchain for record, not truth & 
\textcolor{red}{$\times$} Requires agent approval & 
\textcolor{red}{$\times$} Brokers, title, escrow intact & 
\textcolor{orange}{\textbf{Partially aligned}} \\
\hline
\textbf{RealT} & 
\textcolor{orange}{$\sim$} Ethereum token layer only & 
\textcolor{orange}{$\sim$} Blockchain for token, not legal trust & 
\textcolor{red}{$\times$} Walled garden (KYC/AML) & 
\textcolor{red}{$\times$} Third-party managed assets & 
\textcolor{red}{\textbf{Not aligned}} \\
\hline
\textbf{Lofty.ai} & 
\textcolor{orange}{$\sim$} Algorand-based tokens & 
\textcolor{orange}{$\sim$} Partial automation only & 
\textcolor{red}{$\times$} Platform access only & 
\textcolor{red}{$\times$} Centralized asset control & 
\textcolor{red}{\textbf{Not aligned}} \\
\hline
\textbf{Landshare} & 
\textcolor{orange}{$\sim$} BSC-based tokenization & 
\textcolor{orange}{$\sim$} Staking for DeFi, not property & 
\textcolor{red}{$\times$} Controlled via dApp & 
\textcolor{red}{$\times$} Traditional ownership retained & 
\textcolor{red}{\textbf{Not aligned}} \\
\hline
\textbf{Provenance} & 
\textcolor{red}{$\times$} Permissioned network for financial institutions & 
\textcolor{orange}{$\sim$} Shared ledger but trusted parties remain & 
\textcolor{red}{$\times$} Requires institutional approval & 
\textcolor{orange}{$\sim$} Reduces some costs but preserves gatekeeping & 
\textcolor{red}{\textbf{Not aligned}} \\
\hline
\end{tabular}
\caption{Comparison of Real Estate Blockchain Projects Against Decentralized Design Principles}
\end{table}

Only Elephant Protocol fully embraces decentralization: eliminating intermediaries, enabling trustless validation, and granting open access to all participants. Other projects, including Provenance's institutional securitization focus, maintain dependency on gatekeepers, centralized controls, or regulatory frameworks that contradict the ethos of user sovereignty.

Provenance exemplifies the common pattern of 'blockchain-as-efficiency-tool' rather than 'blockchain-as-empowerment-platform.' While it achieves cost savings for financial institutions, it preserves the fundamental power structures that Andreas Antonopoulos argued blockchain should eliminate. This represents blockchain optimization of gatekeeping rather than its removal.

This distinction matters. Tokenization alone doesn't disrupt real estate's structural inefficiencies. To unlock blockchain's true impact, platforms must be decentralized by design—not merely in branding.

Elephant Protocol demonstrates how blockchain can genuinely replace traditional infrastructure, not reinforce it. Its architecture shows that meaningful transformation is possible when systems are built from first principles rather than retrofitted for optics.